### 2025-09-29 src/articles/article3.qmd
Merge treasury, housing, and scholarship updates (#2)
Fixing typos, adding the previously passed scholarship awards & updates and the Spring 2025 housing bylaw changed.

1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary in accordance with Article V, Section 2, Item j.1 of the IBL.
1. A brother who has three unexcused absences throughout the semester will be {{< var glossary.staggard >}}.
1. A brother who has four unexcused absences throughout the semester will be placed on {{< var glossary.probation >}} until the end of the semester.
1. A brother who has seven unexcused absences throughout the semester will be brought up for standards by the Secretary with the possibility of suspension.

>>>>

1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary in accordance with Article V, Section 2, Item j.1 of the {{< var acronym.ibl >}}.
1. A brother who has three unexcused absences throughout the semester will be {{< var glossary.staggard >}}.
1. A brother who has four unexcused absences throughout the semester will be placed on {{< var glossary.probation >}} until the end of the semester.
1. A brother who has seven unexcused absences throughout the semester will be brought up for standards by the Secretary with the possibility of suspension.

### 2025-09-29 src/articles/article4.qmd
Merge treasury, housing, and scholarship updates (#2)
Fixing typos, adding the previously passed scholarship awards & updates and the Spring 2025 housing bylaw changed.

1. All brothers eligible to vote must vote.
1. Only active brothers who are not on {{< var glossary.probation >}} or {{< var glossary.financial-probation >}} are eligible to vote.
1. Brothers must be present for all of the discussion on a motion in order to be eligible to vote on that motion.
1. A brother not required to pay local dues is ineligible to vote.
1. Unless specified in @sec-art-N8IIFY4C, or explicitly voted on by {{< var glossary.simple-majority >}}, the method of voting will be by a counted show of hands.

@@

1. The following votes will be performed by ballot:
   a. New Members for Initiation
   b. Officer Elections
   c. To overturn an Executive Council ({{< var acronyms.ec >}}) Interpretation of the bylaws (@sec-art-EXPT5HOU)
   d. At a suspension trial
   e. To retain a candidate who was not initiated the previous semester

1. {{< var glossary.ballot >}}ing
   a. The Second Guard and the Chaplain will collect and count the {{< var glossary.ballot >}}s.
   b. The chaplain will confirm the count and repeat the results to the presiding officer.
   c. No brother may count the {{< var glossary.ballot >}}s for a matter related to himself.
   d. In the case of absence, conflict of interest, or at the discretion of the chair, the chair may appoint a brother to collect and count the {{< var glossary.ballot >}}s.

1. New Members for Initiation
   a. {{< var glossary.ballot >}}ing on New Members for Initiation will be in accordance with the International Bylaws ({{< var acronyms.ibl >}}) of Theta Chi Fraternity, Article VI, Section 4, paragraph d.
   b. New Members must be approved by a ¾ vote of eligible voting members of the active chapter to be initiated.

1. Officer Elections
   a. Officers will be elected by {{< var glossary.simple-majority >}} vote.
   b. In the case that no nominee receives a {{< var glossary.simple-majority >}}, there will immediately be another vote between all candidates who received the two highest counts of votes.\
   c. Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for {{< var acronyms.cab >}} interviews.

>>>>

1. All brothers eligible to vote must vote.
1. Only active brothers who are required to pay local dues and are not on {{< var glossary.probation >}} or {{< var glossary.financial-probation >}} are eligible to vote.
1. Brothers must be present for all of the discussion on a motion in order to be eligible to vote on that motion.
1. Unless specified in @sec-art-N8IIFY4C, or explicitly voted on by {{< var glossary.simple-majority >}}, the method of voting will be by a counted show of hands.

@@

1. The following votes will be performed by ballot:
   a. New Members for Initiation
   a. Officer Elections
   a. To overturn an Executive Council ({{< var acronyms.ec >}}) Interpretation of the bylaws (@sec-art-EXPT5HOU)
   a. At a suspension trial

1. {{< var glossary.ballot >}}ing
   a. The Second Guard and the Chaplain will collect and count the {{< var glossary.ballot >}}s.
   a. The chaplain will confirm the count and repeat the results to the presiding officer.
   a. No brother may count the {{< var glossary.ballot >}}s for a matter related to himself.
   a. In the case of absence, conflict of interest, or at the discretion of the chair, the chair may appoint a brother to collect and count the {{< var glossary.ballot >}}s.

1. New Members for Initiation
   a. {{< var glossary.ballot >}}ing on New Members for Initiation will be in accordance with the International Bylaws ({{< var acronyms.ibl >}}) of Theta Chi Fraternity, Article VI, Section 4, paragraph d.
   a. New Members must be approved by a ¾ vote of eligible voting members of the active chapter - including those who are not present - to be initiated.

1. Officer Elections
   a. Officers will be elected by {{< var glossary.simple-majority >}} vote.
   a. In the case that no nominee receives a {{< var glossary.simple-majority >}}, there will immediately be another vote between all candidates who received the two highest counts of votes.\
   a. Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for {{< var acronyms.cab >}} interviews.

### 2025-09-29 src/articles/article5.qmd
Merge treasury, housing, and scholarship updates (#2)
Fixing typos, adding the previously passed scholarship awards & updates and the Spring 2025 housing bylaw changed.

1. Vice President of Health and Safety
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph c.
   a. Plans and oversees a yearly community outreach event regarding health and safety.
   a. Serves as a liaison between the chapter and community health services.
   a. Organizes events on 7 topics, 2 of which are available to the greater public, on Health and Safety for the chapter per academic year.
   a. Maintains house medical kit.
   a. Serves as a member of {{< var acronyms.ec >}}.
   a. Serves as chair of the Health and Safety Committee.
   a. Must live in the house.

1. Secretary
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph d.
   a. Records attendance and enforces the standards for attendance in @sec-art-BUK07FVL.
   a. Serves as Secretary of {{< var acronyms.ec >}}.
   a. Collects all legislation, Bylaw amendments, and Officer Reports.
   a. Sets the agenda for chapter meetings according to the {{< var acronyms.ibl >}} Article V, Section 8, paragraph d.
   a. Maintains the mailbox and mail closet.
   a. Will create a contact list for the chapter which includes contact information of brothers advisors, Greek Life, and emergency services.
   a. Handles registration of Pledges, requests for initiation, and the recording of new initiates.

1. Treasurer
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph e.
   a. Is accountable to the Alumni Corporation.
   a. Collects all feeds, dues, and fines.
   a. Records all transactions made by the chapter.
   a. Will provide a written report at the request of any brother. The report will include all payments paid out, all monies received, current bank account balances, and budget updates.
   a. Keeps private all individual account balances except from the brother whose account it is and {{< var acronyms.ec >}}.
   a. Issues enumerated bills for all brothers and New Members at least three times a semester unless otherwise decided by the chapter.
   a. Announces the names of all members on {{< var glossary.financial-probation >}} at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
   a. Will create a budget following the process outlined in @sec-art-GD7C1K2U.\
   a. Ensures compliance with the General Rules for chapter finances outlined in @sec-art-SKY8T9UM.
   a. Will propose a housing contract to the chapter by the last chapter meeting of each semester with a final version to be approved at the first chapter meeting of the next semester.
   a. Will ensure that all brothers living in the house have signed a housing contract by the second chapter meeting of each semester.
   a. Maintains an emergency fund of no less than $3000 and can withdraw money from the fund only with the authorization of two of the three highest officers.
   a. Will meet with the Alumni Financial Advisor at least twice each semester.
   a. Will file taxes at least two weeks before the filing deadline each year.
   a. Will ensure that taxes will be reviewed by the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}} no later than one month before the filing deadline.
   a. Will send taxes by certified mail, and will distribute this certification to the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}}.
   a. Will retain a physical and electronic backup of financial records for no fewer than five years.
   a. Maintain a changelog of the budget.
   a. Give a monthly financial report to the chapter and deliver the report to {{< var acronyms.cab >}}.
   a. The Treasurer cannot be elected or appointed to a position which has permission to spend from the budget.
   a. Cannot be elected to another position during their term.
   a. A candidate for the position of Treasurer must be interviewed by the {{< var acronyms.cab >}} prior to the election. A {{< var glossary.simple-majority >}} vote of the {{< var acronyms.cab >}} may veto that candidate. This veto can be overruled by a {{< var glossary.supermajority >}} vote of the chapter. Failure for {{< var acronyms.cab >}} to meet with a candidate prior to elections will be interpreted as {{< var acronyms.cab >}} waiving their right to interview the candidate.
   a. Serves as a member of {{< var acronyms.ec >}}.
   a. Must live in the house.

1. Marshal
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph f.
   a. Will submit a plan as Temporary Legislation that expires at the end of the current semester for their office by the first chapter meeting of the semester of their term.
   a. Will reserve a location for initiation.
   a. Will organize a bid acceptance dinner and the bid acceptance ceremony.
   a. Serves as a member of {{< var acronyms.ec >}}.
   a. Must live in the house.

@@

1. Philanthropy and Service Chair
   a. Serves as chair of the Philanthropy and Service Committee.
   a. Ensures the chapter meets the Greek Life goals for service.
   a. Informs the chapter of service and philanthropy opportunities.
   a. Serves as a member of {{< var acronyms.ccc >}}.

>>>>

1. Vice President of Health and Safety
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph c.
   a. Plans and oversees a yearly community outreach event regarding health and safety.
   a. Serves as a liaison between the chapter and community health services.
   a. Organizes events on 5 topics, 2 of which are available to the greater public, on Health and Safety for the chapter per academic year in accordance with the five areas of Sacred Purpose.
   a. Maintains house medical kit.
   a. Serves as a member of {{< var acronyms.ec >}}.
   a. Serves as chair of the Health and Safety Committee.
   a. Must live in the house.

1. Secretary
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph d.
   a. Records attendance and enforces the standards for attendance in @sec-art-BUK07FVL.
   a. Serves as Secretary of {{< var acronyms.ec >}}.
   a. Collects all legislation, Bylaw amendments, and Officer Reports.
   a. Sets the agenda for chapter meetings according to the {{< var acronyms.ibl >}} Article V, Section 8, paragraph d.
   a. Maintains the mailbox and mail closet.
   a. Will create a contact list for the chapter which includes contact information of brothers advisors, Greek Life, and emergency services.
   a. Handles registration of Pledges, requests for initiation, and the recording of new initiates.
   a. Fills out Greek Life and International Headquarters (IHQ) awards that are due in their term.
   a. Releases a weekly TWIOX (This Week in Theta Chi) newsletter to the alumni mailing list

1. Treasurer
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph e.
   a. Is accountable to the Alumni Corporation.
   a. Collects all feeds, dues, and fines.
   a. Records all transactions made by the chapter.
   a. Will provide a written report at the request of any brother which includes all payments paid out, all monies received, current bank account balances, and budget updates.
   a. Keeps private all individual account balances except from the brother whose account it is and {{< var acronyms.ec >}}.
   a. Issues enumerated bills for all brothers and New Members at least three times a semester unless otherwise decided by the chapter.
   a. Announces the names of all members on {{< var glossary.financial-probation >}} at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
   a. Will create a budget following the process outlined in @sec-art-GD7C1K2U.\
   a. Ensures compliance with the General Rules for chapter finances outlined in @sec-art-SKY8T9UM.
   a. Will propose a housing contract to the chapter by the last chapter meeting of each semester with a final version to be approved at the first chapter meeting of the next semester.
   a. Will ensure that all brothers living in the house have signed a housing contract by the second chapter meeting of each semester.
   a. Maintains an emergency fund of no less than $3000 and can withdraw money from the fund only with the authorization of two of the three highest officers.
   a. Will meet with the Alumni Financial Advisor at least twice each semester.
   a. Will file taxes at least two weeks before the filing deadline each year.
   a. Will ensure that taxes will be reviewed by the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}} no later than one month before the filing deadline.
   a. Will send taxes by certified mail, and will distribute this certification to the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}}.
   a. Will retain a physical and electronic backup of financial records for no fewer than five years.
   a. Maintain a changelog of the budget.
   a. Give a monthly financial report to the chapter and deliver the report to {{< var acronyms.cab >}}.
   a. The Treasurer cannot be elected or appointed to a position which has permission to spend from the budget.
   a. Cannot be elected to another position during their term.
   a. A candidate for the position of Treasurer must be interviewed by the {{< var acronyms.cab >}} prior to the election. A {{< var glossary.simple-majority >}} vote of the {{< var acronyms.cab >}} may veto that candidate. This veto can be overruled by a {{< var glossary.supermajority >}} vote of the chapter. Failure for {{< var acronyms.cab >}} to meet with a candidate prior to elections will be interpreted as {{< var acronyms.cab >}} waiving their right to interview the candidate.
   a. Serves as a member of {{< var acronyms.ec >}}.
   a. Must live in the house.

1. Marshal
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph f.
   a. Will submit a Marshal Plan as Temporary Legislation that expires at the end of the current semester for their office by the first chapter meeting of the semester of their term.
   a. Will reserve a location for initiation.
   a. Will organize a bid acceptance dinner and the bid acceptance ceremony.
   a. Serves as a member of {{< var acronyms.ec >}}.
   a. Must live in the house.

@@

1. Philanthropy and Service Chair
   a. Serves as chair of the Philanthropy and Service Committee.
   a. Ensures the chapter meets the Greek Life goals for service and philanthropy.
   a. Informs the chapter of service and philanthropy opportunities.
   a. Serves as a member of {{< var acronyms.ccc >}}.
